Data Hygiene Gotchas

### 2017-01-17 articles/data_hygiene.Rmd
data science advice

---
title: "Data Hygiene Gotchas"
author: "Ming-Yu Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

- [Common data preparation mistakes and how to avoid them](http://www.analyticsvidhya.com/blog/2013/08/common-data-preparation-mistakes-avoid-them/)
- [Webinar: Enhance Predictive Modeling with Better Data Preparation](http://www.datasciencecentral.com/video/enhance-predictive-modeling-with-better-data-preparation)
- [Non-Mathematical Feature Engineering techniques for Data Science](https://codesachin.wordpress.com/2016/06/25/non-mathematical-feature-engineering-techniques-for-data-science/)
- [Simple Methods to deal with Categorical Variables in Predictive Modeling](http://www.analyticsvidhya.com/blog/2015/11/easy-methods-deal-categorical-variables-predictive-modeling/)

>>>>

---
title: "Data Hygiene Gotchas"
author: "Ethen Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

- [Webinar: Enhance Predictive Modeling with Better Data Preparation](http://www.datasciencecentral.com/video/enhance-predictive-modeling-with-better-data-preparation)
- [Blog: Common data preparation mistakes and how to avoid them](http://www.analyticsvidhya.com/blog/2013/08/common-data-preparation-mistakes-avoid-them/)
- [Blog: Non-Mathematical Feature Engineering techniques for Data Science](https://codesachin.wordpress.com/2016/06/25/non-mathematical-feature-engineering-techniques-for-data-science/)
- [Blog: Simple Methods to deal with Categorical Variables in Predictive Modeling](http://www.analyticsvidhya.com/blog/2015/11/easy-methods-deal-categorical-variables-predictive-modeling/)
